### 2019-05-22 doc/leader/versions.tex
added some todos and fixed version

\fontsize{10pt}{18pt}\selectfont
\begin{tabbing}
xxxxxxxxxxx\=xxxxxxxxxxxxxxx\=xxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
Version	\> Date	\> Status			\> Remarks		\\
0.1	\> 01.08.2013	\> Draft		\> Lorem ipsum dolor sit amet	\\	
0.2	\> 21.08.2013	\> Draft		\> Phasellus scelerisque	\\ 
0.3	\> 02.09.2013	\> Draft		\> Donec eget aliquam urna. Lorem ipsum dolor sit amet	\\ 
1.0	\> 26.01.2014	\> Final		\> Lorem ipsum dolor sit ametPhasellus scelerisque, leo sed iaculis ornare 	\\ 
1.1	\> 31.01.2014	\> Correction	\> Layout changed	\\
1.2	\> 07.02.2014	\> Addition		\> Chapter 1.1 extended	\\
\end{tabbing}

>>>>

\fontsize{10pt}{18pt}\selectfont
\begin{tabbing}
xxxxxxxxxxx\=xxxxxxxxxxxxxxx\=xxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
Version	\> Date	\> Status			\> Remarks		\\
1.0	\> TODO fix this	\> Final		\> Final Version 	\\
\end{tabbing}
